Project Light

### 2015-09-03 paper/paper.tex
make notes for android app subsection

@@

functionality, flashlight, limitations

>>>>

In the following sections, both the implementation of the Android application and the Contiki process are described in more detail.

@@

- two versions with different strengths
- first web app deployed with cordova as native app
- functionality: almost all parameters were adjustable, i.e. length of one bit, length of initialization phase, initialization-pattern, start-pattern, if hamming-encoding should be used.
- biggest advantage: runs also in browser an easily portable to iPhone/windows phone/...
- but also fast prototyping
- downsides: javascript timer inaccuracy
- Flash light reacted very slowly
- white and dark screen background only possible way to go

-figure: both screenshots next to each other

- second version: native android app
- still no real time possible (source!), but smaller stack (no phoneGap runtime and javascript interpreter required)
- native readjusting timer: if one event fires too late, delay won't add up
- flash light works as good as background flickering
- clearer design because of less controllable parameters: just bit-length and switches to use flashlight and hamming-encoding. (better for end users)
